New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2024-10-14 jso.tex
Table 1 before Table 2

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, toprule=.15mm, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, coltitle=black, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, colback=white, opacitybacktitle=0.6, bottomrule=.15mm, titlerule=0mm, rightrule=.15mm, arc=.35mm, bottomtitle=1mm, left=2mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, toprule=.15mm, colback=white, opacityback=0, left=2mm, bottomtitle=1mm, breakable, arc=.35mm, bottomrule=.15mm, titlerule=0mm, leftrule=.75mm, toptitle=1mm, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, title={Algorithm: Jellyfish Optimizer Pseudo Code}, coltitle=black]
